\documentclass[11pt]{article} 
\usepackage[T1]{fontenc}
\usepackage{calc}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{fancyheadings}

\usepackage{graphicx}
\usepackage{color}
\usepackage{rotating}
\usepackage{harvard}
\usepackage{aer}
\usepackage{aertt}
\usepackage{verbatim}

\setlength{\voffset}{0in}
\setlength{\topmargin}{0pt}
\setlength{\hoffset}{0pt}
\setlength{\oddsidemargin}{0pt}
\setlength{\headheight}{0pt}
\setlength{\headsep}{0in}
\setlength{\marginparsep}{0pt}
\setlength{\marginparwidth}{0pt}
\setlength{\marginparpush}{0pt}
\setlength{\footskip}{.1in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\parindent}{0in}
\setlength{\parskip}{1pc}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\prbf}[1]{\textbf{#1}}
\newcommand{\prit}[1]{\textit{#1}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bdm}{\begin{displaymath}}
\newcommand{\edm}{\end{displaymath}}
\newcommand{\script}[1]{\begin{cal}#1\end{cal}}
\newcommand{\citee}[1]{\citename{#1} (\citeyear{#1})}
\newcommand{\h}[1]{\hat{#1}}
\newcommand{\ds}{\displaystyle}

\renewcommand{\refname}{}

\pagestyle{empty}
\begin{document}

\today

Dear Editors:

Thank you for inviting a revision of our paper, ``A life insurance deterrent to risky behavior in Africa'' to \textit{Journal of Policy Modeling}. 

In response to your letter, we have strengthened the policy discussion in the paper by rewriting the introduction and adding a new section dedicated solely to policy discussion.  This new section appears immediately after the introduction, and we revised our introduction and wrote this section in such a way that limited the additional length of the paper.  Indeed the purpose of the paper is to model an HIV/AIDS prevention policy and to explore its efficacy, but the evaluation of the policy in the context of the model necessarily comes late in the paper.  We believe our revision more clearly communicates this purpose, and appropriately sets the tone of the paper as an exploration into a government policy proposal.

Thank you for the suggestion to consider more \textit{Journal of Policy Modeling} papers.  Upon a more careful review of contributions published in the journal, we found several papers to cite that strengthened both the motivation for the paper and a deeper discussion on policy.  The following papers are cited in this revision: 

\nocite{CHR1994}\nocite{Arndt2003}\nocite{HC1994}\nocite{RVP2002}\nocite{RS2008}\nocite{GV2001}
\vspace*{-4pc}
\bibliographystyle{econometrica}
\bibliography{aids_ins}

We find our paper is improved with with these revisions based on your recommendations.  We hope you conclude the same.  We look forward learning your impression and we welcome any additional feedback.

Sincerely,

Pedro de Araujo\\
James Murray

\end{document}
